The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-12-02 Paper.qmd
Working toward anonymized data

```{r setup, include=FALSE}
source("recode.R")
source("dictionaries.R")
source("dataprep.R")
# source("dataprepPublic.R")
source("analysis.R")
# source("analysis2.R") # slow!
```

@@

`{r} xfun::numbers_to_words(n_distinct(utila_df$householdID), cap=T)` primary caretakers (females = `{r} table(caregiverSex)[1]`, males = `{r} table(caregiverSex)[2]`, missing sex = `{r} sum(is.na(caregiverSex))`) took the survey and provided signaling data for at least one child. `{r} xfun::numbers_to_words(nrow(utila_df), cap=T)` children had frequency data for at least one signal, with `{r} nrow(modeldf_FULLSIG)` having data for all three. Among those with at least one record of signaling frequency, `{r} sex_table[1]` were female and `{r} sex_table[2]` were male. For summary statistics of study variables see @tbl-sumtab_combined and @tbl-sumtab_factors.

>>>>

```{r setup, include=FALSE}
source("recode.R")
source("dictionaries.R")
# source("dataprep.R")
source("dataprepPublic.R")
source("analysis.R")
# source("analysis2.R") # Generates many plots. Slow!
```

@@

`{r} xfun::numbers_to_words(n_distinct(utila_df$householdID), cap=T)` primary caretakers (females = `{r} table(caregiverSex)[1]`, males = `{r} table(caregiverSex)[2]`, missing sex = `{r} sum(is.na(caregiverSex))`) took the survey and provided signaling data for at least one child. `{r} xfun::numbers_to_words(nrow(utila_df), cap=T)` children had frequency data for at least one signal, with `{r} nrow(utila_FULLSIG)` having data for all three. Among those with at least one record of signaling frequency, `{r} sex_table[1]` were female and `{r} sex_table[2]` were male. For summary statistics of study variables see @tbl-sumtab_combined and @tbl-sumtab_factors.
